%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt,notitlepage]{article}
\usepackage{cite}
\usepackage{amsmath,amssymb}
\usepackage{comment}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{bm}
\usepackage{tgheros} % Use Helvetica
\usepackage{fancyhdr}
\usepackage[dvipdfmx]{graphicx, hyperref, xcolor}

%%%%% Hyperref %%%%%
\definecolor{orangered}{HTML}{FF4500}
\definecolor{crimson}{HTML}{DC143C}
\definecolor{rossoferrari}{HTML}{D9073D}
\definecolor{steelblue}{HTML}{4682B4}
\definecolor{mediumblue}{HTML}{0000CD}
\definecolor{forestgreen}{HTML}{228B22}
\hypersetup{% hyperref option list
setpagesize=false,
bookmarksnumbered=true,%
bookmarksopen=true,%
colorlinks=true,%
linkcolor=orangered,
urlcolor=steelblue,
citecolor=steelblue,
}

%%%%% spacing %%%%%
\renewcommand{\baselinestretch}{1.5}

%%%%% Geometry %%%%%
\usepackage[height=21.5cm,width=16.5cm,centering]{geometry}

%%%%% New commands %%%%%
\newcommand{\Slash}[1]{{\ooalign{\hfil/\hfil\crcr$#1$}}}
\newcommand{\hyphen}{\,\mathchar`-\mathchar`-\,}

\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
%\renewcommand{\thefootnote}{\#\arabic{footnote}}
\renewcommand{\thefootnote}{$\natural$\arabic{footnote}}
\setcounter{footnote}{0}

%%%%% header %%%%%
\pagestyle{fancy}
\rhead[Research statement $-$ So Chigusa]{Research statement $-$ So Chigusa}
\renewcommand{\headrulewidth}{0pt} % vanishing hr
\renewcommand{\footrulewidth}{0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%    remove the following commands when finalizing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\rem#1{ {\bf\textcolor{red}{($\clubsuit$ #1 $\clubsuit$)}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\allowdisplaybreaks[1]

\title{\vspace*{-3cm}Research statement}
\author{\textbf{So Chigusa}}
\date{\vspace*{-4mm}\textit{Ph.D. candidate in Physics at University of Tokyo}}

\begin{document}
\maketitle

My research interests lie in the phenomenology of a broad range of models beyond the standard model (SM) of particle physics.
In spite of the great success of the SM, there remain many problems that cannot be solved within the SM.
These problems include, for example, the existence of the dark matter (DM), naturalness of the electroweak (EW) scale, structure of the gauge symmetries, and origin of the quark and lepton families.
To answer one or several of them, many interesting models are proposed such as the minimally supersymmetric standard model (MSSM), grand unified theory (GUT), flavor symmetry, and so on.

In my opinion, many of these models are still incomplete, since they sometimes have inconsistencies with experimental results or cosmological observations, or have too many degree of freedom to obtain non-trivial prediction.
Thus, in my research career, I seek ways to test the models and, at the same time, try to construct new models or mechanisms that solve the above problems in a simple and resonable way.
My main achievements described in the following are categolized as
\vspace{-1.3mm}
\begin{itemize}
  \setlength{\parskip}{0mm}
  \setlength{\itemsep}{1mm}
  \item precise calculation of the EW vacuum decay rate to test the SM and beyond.
  \item analysis of the search for the MSSM particles using future hadron colliders.
  \item construction of cosomologically viable models with discrete flavor symmetry.
  \item search for the parameter space of the MSSM compatible with the GUT prediction.
\end{itemize}

\vspace*{-2mm}
\subsection*{Achievements so far}

During the last few years, I have been developing the next-to-leading order calculation of the decay rate of the EW vacuum.
This approach is powerful because it is applicable to many models that contain some additional fields and/or couplings to the SM Higgs boson even when new particles are too heavy to be accessed using any ongoing or planned experiment.
In this topics, I made several achievements:
\vspace{-1.3mm}
\begin{itemize}
  \setlength{\parskip}{0mm}
  \setlength{\itemsep}{1mm}
  \item
    I considered the SM and gave a proper way to treat the flat direction of the Euclidean action related to the classical conformal invariance.
    This enabled us to precisely evaluate the decay rate with error estimations. ([9] of my publications)
  \item
    I considered models with new particles that couple to the SM Higgs and obtained severe constraints on their couplings and masses from the EW vacuum stability. [8]
  \item
    I proposed a new way based on the gradient flow to numerically evaluate the multi-field bounce configuration.
    This method is useful for the next-leading order calculation of the vacuum decay rate when the asymptotic behavior of the bounce is needed. [1]
\end{itemize}

It is also important to use the collider experiments to search for the new physics.
In particular, hadron colliders provide a huge amount of data, under which a hint of the new physics may be buried.
To fully use the data, it is necessary to develop a proper physics quantity or a wise way to extract the signal of a new particle.
I have adopted several ways to tackle this difficult problem using future hadron colliders.
\vspace{-1.3mm}
\begin{itemize}
  \setlength{\parskip}{0mm}
  \setlength{\itemsep}{1mm}
  \item
    I focused on the parmeter space of the MSSM where wino is the lightest new physics particle.
    I used the so-called disappearing track signal caused by sufficiently long-lived charged winos to reduce background events.
    In this work, I collaborated with several experimentalists and seeked a possibility of using track information to fully reconstruct the event kinematics and to determine the masses of new particles [4].
  \item
    When we search for the Higgsino-like state in the MSSM, the charged component is short-lived and the track information is not available.
    To handle this case, I focused on the lepton pair production process that is affected by Higgsino at the one-loop level and developed a way to use the energy dependence of the cross section to reduce the systematic uncertainties.
    As a result, I obtained the best limit so far for Higgsino [3,5].
\end{itemize}

It is another interesting way of research to build a new physics model.
All problems in the SM are hints of the theory of everything, which is our ultimate goal.
By providing simple solutions to them, we can enrich our knowledge about what could be there beyond the SM.
So far, I worked on discrete flavor symmetry and GUT models that provide a unified description of SM fermion families and gauge symmetries, respectively.
\vspace{-1.3mm}
\begin{itemize}
  \setlength{\parskip}{0mm}
  \setlength{\itemsep}{1mm}
  \item
    In models with spontaneously broken discrete symmetries, domain walls may be formed that will eventually dominate the energy of our universe.
    To avoid this problem, I constructed several models with discrete flavor symmetry in which cosmological dynamics does not lead to the formation of the stable domain wall and the most recent observation of the neutrino mixing angles are correctly predicted at the same time. [2,6,7]
  \item
    I focused on the supersymmetric $\mathrm{SU}(5)$ GUT and looked for the parameter space where the unification of the Yukawa coupling constants, which is the prediction of the model, is achieved.
    I also considered the effect of extra matter fields by calculating their contribution to the renormalization group equations and found some parameter space that gives a consistent prediction. [10,11]
\end{itemize}

\vspace*{-2mm}
\subsection*{Future plans}

%In the near future, I will extend our calculation of the vacuum decay rate to models with several scalar fields involved in the bounce configuration.
%This allows us to evaluate the vacuum decay rate in various complicated models such as the MSSM, and to constrain the parameter space even when the new particles are beyond the experimental reach.
%For the generic models with several mass scales, the multi-scale nature of the bounce makes the numerical calculation difficult.
%Therefore, another possible future direction is to develop an algorithm to adaptively adjust the lattice spacing for the fast and accurate computation.
%Regarding the collider search, I will apply our method to the pair production process of gauge bosons.
%This analysis results in the increase in statistics, which may allow us to reach the Higgsino mass preferred from the DM relic abundance.
%Another possibility is to study loop topologies different from the vacuum polarization.
%Through the classification of the signal shape for each topology, I will look for new particles to which our method can be applied.
%Finally, the future planned lepton colliders such as ILC and CLIC also bring us some exciting possibilities.
%Since they provide more precise measurements in lower energy scale compared with hadron colliders, it will be efficient to analyze the new particles effect using the effective field theory approach.
%I will provide some model-independent constraints on EWIMPs through the precise measurement at lepton colliders.

Now it is an exciting time with many ongoing and future planned experiments that provide a huge number of hints of the new physics.
The results of these experiments will guide future theoretical works.
At the same time, a great deal of effort is devoted to developing new approaches to the problems of the SM and new techniques to extract the information from experimental results.
As a young researcher at this time, I am eager to engage in fields of great progress and to keep seeking a trace of the new physics.

First I will extend my calculation of the EW vacuum decay rate to more complex models with several scalar fields involved in the bounce.
After the extension, there will be numerous models to which my calculation is applicable.
I will also consider how we can take account of the thermal effect and effect of gravity both of which may drastically change the situation.

Regarding the collider search, I will analyze the pair production process of gauge bosons to search for Higgsino.
This analysis combined with my previous one results in the increase in statistics, which may allow us to reach the Higgsino mass preferred from the DM relic abundance.
Another possibility is to study loop topologies different from the vacuum polarization.
Through the classification of the energy dependence of the cross section for each topology, I will look for different particles to which our method can be applied.

Recently, a lot of techniques are developed that enable us to systematically analyze the collider data.
These include, for example, the effective field theory (EFT) and machine learning.
I am interested in considering how to use them to enlarge the reach of the collider experiments.
The EFT technique is also useful for the evaluation of the event rate in DM direct detection experiments.
Since there are many models with a broad range of DM mass in the literature, I will try to obtain some systematic treatment applicable for many models and to suggest new experiments for the mass region unconstrained so far.
\rem{Some concrete application here}

After all, the fields of great interest highly depends on the future development of the calculation technique, appearence of new ideas, and results of experiments.
To keep track of the latest trends, I will not restrict myself to studying the same subjects as I have been involved in and have a wide field of view during my research career.

\end{document}
