\documentclass[12pt,notitlepage]{article}
\usepackage{amsmath,amssymb}
\usepackage{bm}
\usepackage{tgheros} % Use Helvetica
\usepackage{fancyhdr}
\usepackage[dvipdfmx]{graphicx, hyperref, xcolor}

\setlength{\textwidth}{16.5cm}
\setlength{\textheight}{21.5cm}
\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}
\setlength{\topmargin}{0cm}
\setlength{\footskip}{0cm}

\renewcommand{\arraystretch}{1.2}
\renewcommand{\baselinestretch}{1.1}

\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}

%%% reference setting %%%
\renewcommand{\refname}{Publications}
\makeatletter
\renewenvironment{thebibliography}[1]
     {\subsection*{\refname} % modified here from section to subsection
      \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
      \list{\@biblabel{\@arabic\c@enumiv}}%
           {\settowidth\labelwidth{\@biblabel{#1}}%
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \@openbib@code
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother

\allowdisplaybreaks[1]

%%%%% header %%%%%
\pagestyle{fancy}
\lhead[]{}
\rhead[Curriculum Vitae $-$ So Chigusa]{Curriculum Vitae $-$ So Chigusa}
\renewcommand{\headrulewidth}{0pt} % vanishing hr

\title{\vspace{-2cm}\textbf{Curriculum Vitae}}
\author{So Chigusa}

\begin{document}
\maketitle

\newcommand{\lsim}{\stackrel{<}{_\sim}}
\newcommand{\gsim}{\stackrel{>}{_\sim}}

\newcommand{\rem}[1]{{$\spadesuit$\bf #1$\spadesuit$}}

\renewcommand{\thefootnote}{\arabic{footnote})}
\setcounter{footnote}{0}

\subsection*{Personal Data}

\vspace{-3mm}
\begin{table}[h]
 \begin{tabular}{ll}
  First Name: & So % (颯)
      \\
  Last Name: & Chigusa % (千草)
      \\
  Date of Birth: & May 22, 1992 \\
  Place of Birth: & Kobe, Japan \\
  Nationality: & Japanese \\
  % Age below
  Age: & 27 \\
  % Age above
  Sex: & Male \\
 \end{tabular}
\end{table}

\vspace{-5mm}
\begin{table}[h]
 \begin{tabular}{ll}
  Affiliation: & University of Tokyo \\
  Postcode: & 113-8654 \\
  Address: & 7-3-1, Hongo, Bunkyo-ku, Tokyo \\
  Phone: & +81-3-5841-4138 \\
  E-mail: &
      \href{mailto:chigusa@hep-th.phys.s.u-tokyo.ac.jp}{chigusa@hep-th.phys.s.u-tokyo.ac.jp}
      \\
  Homepage: & \url{https://sochigusa.bitbucket.io} \\
 \end{tabular}
\end{table}
\vspace{-5mm}

\subsection*{Education}
\vspace{-3mm}
\begin{table}[h]
 \begin{tabular}{lll}
  \hline \hline
  Date & Degree & University \\ \hline
  Mar. 24, 2017 & Master of Science (Physics) & University of Tokyo \\
  Mar. 2015 & Bachelor of Science (Physics) & University of Tokyo \\
  \hline \hline
 \end{tabular}
\end{table}

\newpage
\subsection*{Professional experience}
\vspace{-3mm}
\begin{table}[h]
 \begin{tabular}{ll}
  \begin{tabular}{l}
   Apr. 2015 - Mar. 2020:\\
  \quad
  \end{tabular} &
  \begin{tabular}{l}
   Ph.D. Student, Department of Physics, University of Tokyo\\
   (Dr. Takeo Moroi)
  \end{tabular}
 \end{tabular}
\end{table}
\vspace{-5mm}

\subsection*{Teaching experience}
\vspace{-3mm}
\begin{table}[h]
 \begin{tabular}{ll}
  \begin{tabular}{l}
   Apr. 2015 - Sep. 2015:\\
   \quad
  \end{tabular} &
  \begin{tabular}{l}
   Teaching Assistant for Undergraduate Class ``Quantum Mechanics
   II''\\
   at Department of Physics, University of Tokyo
  \end{tabular}
 \end{tabular}
\end{table}
\vspace{-5mm}

\subsection*{Grants}
\vspace{-3mm}
\begin{table}[h]
 \begin{tabular}{ll}
  \begin{tabular}{l}
   Apr. 2017 - Mar. 2020:\\
   \quad
  \end{tabular} &
  \begin{tabular}{l}
   JSPS, Research Fellowships for Young Scientists (DC1)\\
   Amount: 2800000 JPY
  \end{tabular}\\
  \begin{tabular}{l}
   Oct. 2015 - Mar. 2020:
  \end{tabular} &
  \begin{tabular}{l}
   MEXT, Program for Leading Graduate Schools
  \end{tabular}
 \end{tabular}
\end{table}
\vspace{-5mm}

\subsection*{Honors and Awards}

\begin{enumerate}
 % Awards below
 \item Best Poster Award @ HPNP 2019
 % Awards above
\end{enumerate}

\bibliographystyle{../JHEP}
\bibliography{../pl}
\nocite{*}

\subsection*{Invited Seminar Presentations}

\begin{enumerate}
  \item ``Indirect Studies of Electroweakly Interacting Particles at 100 TeV Hadron Colliders'', Osaka University, July 2019.
  \item ``Indirect Studies of Electroweakly Interacting Particles at 100 TeV Hadron Colliders'', University of Florida, May 2019.
  \item ``Indirect Studies of Electroweakly Interacting Particles at 100 TeV Hadron Colliders'', Florida State University, May 2019.
  \item ``Indirect Studies of Electroweakly Interacting Particles at 100 TeV Hadron Colliders'', KEK, April 2019.
  \item ``Solutions to Domain Wall Problem in Models with Discrete Flavor Symmetry'', Hokkaido University, January 2019.
  \item ``Probing Electroweakly Interacting Massive Particles with Drell-Yan Process at 100 TeV Hadron Colliders'', Nagoya University, October 2018.
\end{enumerate}

\subsection*{Presentations at International Conferences}

\subsubsection*{(Oral)}

\begin{enumerate}
 % Talks below
 \item ``Indirect Studies of Electroweakly Interacting Particles at 100 TeV Hadron Colliders'', Summer Institute 2019, Gangneung, Korea, August 2019.
 \item ``Flowing to the Bounce'', New Higgs Working Group 26, Osaka, August 2019.
 \item ``Indirect Studies of Electroweakly Interacting Particles at 100 TeV Hadron Colliders'', SUSY 2019, Texas, May 2019.
 \item ``Indirect Studies of Electroweakly Interacting Particles at 100 TeV Hadron Colliders'', Pheno 2019, Pittsburgh, May 2019.
 \item ``Flavon Stabilization in Models with Discrete Flavor Symmetry'', KEK-PH 2018 winter, Tsukuba, December 2018.
 \item ``Decay Rate of the Electroweak Vacuum in the Standard Model and Beyond'', Planck 2018, Bonn, May 2018.
 \item ``Bottom-Tau Unification in Supersymmetric Models'', New Physics Forum, IPMU, February 2017.
 \item ``Bottom-Tau unification in Supersymmetric Model with Anomaly-Mediation'', SUSY 2016, Melbourne, July 2016.
 % Talks above
\end{enumerate}

\subsubsection*{(Poster)}

\begin{enumerate}
  \item ``Probing Electroweakly Interacting Massive Particles with Precision Measurements at 100 TeV Hadron Colliders'', HPNP2019, Osaka, February 2019.
\end{enumerate}

\subsection*{Presentations at Domestic Conferences}

\subsubsection*{(Oral)}

\begin{enumerate}
  \item ``Flavon Stabilization without Domain Wall Problem in Discrete Flavor Symmetry Models'', Neutrino Oscillation and Flavor Physics, Nagoya, June 2019.
  \item ``Zero Mode Problem in the Calculation of Decay Rate of the SM Electroweak vacuum'', JPS 2018, Shinshu, September 2018.
  \item ``Bottom-Tau unification in Supersymmetric Model with Anomaly-Mediation'', JPS 2016, Miyazaki, September 2016.
\end{enumerate}

\subsubsection*{(Poster)}

\begin{enumerate}
  \item ``Indirect Search of WIMP Dark Matter at Future 100 TeV Collider'', PPP 2018, Kyoto, August 2018.
  \item ``Bottom Tau Unification in Supersymmetric Models'', PPP 2017, Kyoto, August 2017.
\end{enumerate}

\subsection*{Poster Presentations at International Summer Schools}

\begin{enumerate}
  \item ``Decay Rate of the Electroweak Vacuum in the Standard Model and Beyond'', Cargese Summer School 2018, July 2018.
  \item ``Bottom Tau Unification in Supersymmetric Models'', Les Houches Summer School 2017, July 2017.
\end{enumerate}

\end{document}
