%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt,notitlepage]{article}
\usepackage{cite}
\usepackage{amsmath,amssymb}
\usepackage{comment}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{bm}
\usepackage{tgheros} % Use Helvetica
\usepackage{fancyhdr}
\usepackage[dvipdfmx]{graphicx, hyperref, xcolor}
\usepackage{ifthen}

%%%%% Hyperref %%%%%
\definecolor{orangered}{HTML}{FF4500}
\definecolor{crimson}{HTML}{DC143C}
\definecolor{rossoferrari}{HTML}{D9073D}
\definecolor{steelblue}{HTML}{4682B4}
\definecolor{mediumblue}{HTML}{0000CD}
\definecolor{forestgreen}{HTML}{228B22}
\hypersetup{% hyperref option list
setpagesize=false,
bookmarksnumbered=true,%
bookmarksopen=true,%
colorlinks=true,%
linkcolor=orangered,
urlcolor=steelblue,
citecolor=steelblue,
}

%%%%% spacing %%%%%
\renewcommand{\baselinestretch}{1.5}

%%%%% Geometry %%%%%
\usepackage[height=22.5cm,width=16.5cm,centering]{geometry}

%%%%% New commands %%%%%
\newcommand{\Slash}[1]{{\ooalign{\hfil/\hfil\crcr$#1$}}}
\newcommand{\hyphen}{\,\mathchar`-\mathchar`-\,}

%%%%% Professor Name %%%%%
\def\professorname{John Ellis}
% \def\noprofessorname{} % activate this to use "To whom..."
% \def\fellowship{} % activate this if fellowship
\def\groupname{King's College London} % high energy theory group name if exist
\def\freestyle{} % or free-style

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%    remove the following commands when finalizing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\rem#1{ {\bf\textcolor{red}{($\clubsuit$ #1 $\clubsuit$)}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\allowdisplaybreaks[1]

\title{\vspace*{-3cm}Cover Letter}
\author{\textbf{So Chigusa}}
\date{}

\begin{document}
\maketitle
\thispagestyle{empty}

\ifthenelse{\isundefined{\noprofessorname}}
{Dear Prof. \professorname,}
{To whom it may concern,}

\vspace{3mm}
I would like to inquire whether there is a \ifthenelse{\isundefined{\fellowship}}{postdoctoral}{postdoctoral research fellowship} position in theoretical particle physics\ifthenelse{\isundefined{\groupname}}{\freestyle}{ at \groupname} starting in Fall 2020.
I am currently a graduate student at the University of Tokyo and going to finish my Ph.D. in March 2020.

I am an energetic researcher who enjoys working with people on a broad range of topics.
So far, I have been working on several aspects of the phenomenology of the standard model of the particle physics and beyond.
Firstly, I studied the stability of the electroweak vacuum and gave a proper calculation framework of the next-to-leading order decay rate of the vacuum.
Secondly, I proposed and analyzed several methods to efficiently search for the supersymmetric partners of gauge bosons using future hadron colliders and evaluated their ability to discover a new particle and to measure its properties.
More recently, I obtained a severe constraint on the parameter space of the very light axion-like dark matter using the rotation of the polarization plane of the light emitted from astrophysical sources.
I also considered the cosmological and experimental constraints on models with flavor symmetry and grand unified theories.
In the future, I want to keep seeking a trace of the new physics using the rich knowledge of phenomenology I have acquired during my Ph.D. course.

So I wish to be a postdoctoral fellow at your group and continue my research.
I have asked recommendation letters to the following researchers which will be directly sent to you:
\vspace{-9mm}
\begin{itemize}
  \setlength{\parskip}{1mm}
  \setlength{\itemsep}{0cm}
  \item Prof. Takeo Moroi (Department of Physics, University of Tokyo)
  \item Prof. Koichi Hamaguchi (Department of Physics, University of Tokyo)
  \item Prof. Kazunori Nakayama (Department of Physics, University of Tokyo)
\end{itemize}
\vspace{-2mm}
Please find attached my C.V., research statement, and list of publications.

I am looking forward to hearing from you.

\vspace{3mm}
Sincerely yours,

\vspace{3mm}
So Chigusa

\end{document}
